---
title: "Example_Rmarkdown.md"
author: "Elizabeth Everman"
date: "1/14/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE) 

# Setting include = FALSE hides this code chunk
# Setting echo = TRUE includes code in report
```

## R Markdown

R Markdown can generate 3 types of documents:

- HTML 
- PDF
- MS Word

To preview your document, click:

- Settings
  - Preview in Viewer Pane
    - Knit
    

To change text appearance:

# Biggest
## Smaller
### Small
#### Even Smaller
##### Tiny
###### Why Bother

**bold**

*italics*

~~strikethrough~~

superscript^2^

$$E = mc^2$$

[More R Markdown Help](rmarkdown.rstudo.com)


## Producing a Report:

```{r Libraries, include=TRUE}

# Install the package pacman.
# Then use p_load to load packages and install them if needed.
pacman::p_load(ggplot2, Rmisc)
```


### Analysis of Very Important Iris Characteristics

```{r Datafiles, include=TRUE}
# we will practice with a pre-loaded dataframe:
head(iris)
summary(iris)
```

### Analyses: lm and anova

There is a significant correlation between Sepal length and width.

```{r Correlation between Sepal lengh and width}
# not necessary to use include=TRUE.

sepal_size.lm <- lm(Sepal.Length ~ Sepal.Width, data = iris)
summary(sepal_size.lm)
```

Sepal size varies across the three iris species.

```{r ANOVA: EO Species on Sepal Size}

iris$Sepal.Size <- iris$Sepal.Length * iris$Sepal.Width

species_sepals.aov <- aov(Sepal.Size ~ Species, data = iris)
anova(species_sepals.aov)
```

## Plots of Results:

Including echo=FALSE prevents the plot code from beind printed.


```{r Plot LM, echo=FALSE}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  geom_smooth(method = "lm")

# Customized version:
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  geom_smooth(method = "lm", aes(fill = Species)) +
  xlab("Sepal Length") +
  ylab("Sepal Width") +
  scale_color_manual(values = c("purple", "violet", "pink")) +
  scale_fill_manual(values = c("purple", "violet", "pink")) +
  theme_classic()
```

Bonus function for data analysis:
Rmisc includes summary functions useful for plotting anova results.

```{r Plot ANOVA, echo=FALSE}

sepal_size_summary <- summarySE(data = iris, measurevar = "Sepal.Size", groupvars = "Species", na.rm = TRUE)
sepal_size_summary

ggplot(sepal_size_summary, aes(x = Species, y = Sepal.Size)) +
  geom_errorbar(aes(ymin = Sepal.Size - ci, ymax = Sepal.Size + ci)) +
  geom_point() +
  theme_classic()

ggplot(sepal_size_summary, aes(x = Species, y = Sepal.Size)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = Sepal.Size - ci, ymax = Sepal.Size + ci), width = 0.2) +
  theme_classic()

ggplot(sepal_size_summary, aes(x = Species, y = Sepal.Size, fill = Species)) +
  geom_bar(stat = "identity") +
  geom_point() +
  geom_errorbar(aes(ymin = Sepal.Size - ci, ymax = Sepal.Size + ci), width = 0.2) +
  scale_fill_manual(values = c("purple", "violet", "pink")) +
  annotate("text", label = "*", x = 3, y = 22, size = 10) +
  theme_classic()

```
